\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\overfullrule=0pt
\usepackage[colorlinks=false,draft=false]{hyperref}

\usepackage{xcolor}
% \usepackage{verbatim}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\definecolor{blue}{HTML}{005cc5}
\definecolor{lightblue}{HTML}{126180}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand\fbox{\fcolorbox{red}{white}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheadingBold}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \textbf{}{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



\begin{center}
    {\Huge \scshape \textcolor{blue}{ Sumit Singh}} \\ \vspace{5pt}
    % 123 Street Name, Town, State 12345 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +(91)9870177363 \texttt{|} ~ \href{mailto:sumitsinghtp304@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  sumitsinghtp304@gmail.com} \texttt{|} ~ 
    \href{https://linkedin.com/in/sumit-singh304/}{\raisebox{-0.2\height}\faLinkedin\ sumit-singh304  } \texttt{|} ~
    \href{https://github.com/singh05sumit}{\raisebox{-0.2\height}\faGithub\ github.com/singh05sumit    }
   
    \vspace{-8pt}
\end{center}\vspace{+10pt}

 %-----------PROGRAMMING SKILLS-----------
        \section{\textcolor{blue}{Technical Skills}}
            \vspace{2pt}
        \begin{itemize}[leftmargin=0.0in, label={}]
              \normalsize{\item{
              \textbf{Languages and Databases}{: Python, PostgreSQL} \\
        	 \vspace{4pt}
              \textbf{Libraries}{: Pandas, Numpy, Matplotlib, Seaborn, Scikit-Learn } \\
        	\vspace{4pt}
              \textbf{Visualization tools}{: Advance Excel, Power BI} \\
            \vspace{4pt}
              \textbf{Data Analysis Skills}}{: Data Wrangling, Exploratory Data Analysis, Data Visualization, Applied Statistics, Machine learning Basics, Extract Transform Load (ETL) } \\
            }
        \end{itemize}





%-----------EXPERIENCE-----------
\section{\Large \textcolor{blue}{Experience}}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Workgen Solution Pvt Ltd}{}
      {Operation Executive}{June'22 -- Nov'22}
      \resumeItemListStart
        \resumeItem{Maintained daily workforce records and compiled comprehensive reports,resulting in improvement in data accuracy for
senior management’s decision making.}
        \resumeItem{Conducted background verifications for over \textbf{\textcolor{black}{125,000+}} new and current employees, reducing theft and criminal activity and improving overall security by \textbf{\textcolor{black}{30\%}} at industrial premises.
        \resumeItem{Analyzed and monitored \textbf{\textcolor{black}{shifts data}} to confirm slot availability for over \textbf{\textcolor{black}{50,000+}} store workers, leading to a \textbf{\textcolor{black}{25\%}} reduction in logistical and shift change issues.}}
        \resumeItemListEnd
        
         \vspace{+6pt}
        

    \resumeSubheading
      {Mitsui O.S.K Lines Pvt Ltd}{}
      {Assistant Engineer}{Aug'17 - Jan '19}
         \resumeItemListStart 
            \resumeItem{Engineered daily operations of ship machinery as a Junior Engineer on a container vessel,enhancing system performance and reducing downtime by \textbf{\textcolor{black}{20\%}. }}
            \resumeItem{Participated in all safety and environmental drills as directed by the Captain, ensuring compliance and enhancing overall emergency preparedness.}
            \resumeItem{Diagnosed and resolved critical issues during a scheduled maintenance period of engine room machinery, collaborating with senior engineers to achieve \textbf{\textcolor{black}{100\%}} operational efficiency and prevent project delays.
}}
          \resumeItemListEnd 
           
                 \vspace{+6pt}
           
    % \resumeSubheading
    %   {Navidrome}{}
    %   {Open Source Contributer}{Feb'21 -- May'21}
    %      \resumeItemListStart
    %      \resumeItem{Multiple \href{https://github.com/navidrome/navidrome/pulls?q=is\%3Apr+author\%3Arishabh-malhotraa}{\underline{pull requests}} and \href{https://github.com/navidrome/navidrome/issues?q=is\%3Aissue+author\%3ARishabh-malhotraa+}{\underline{issues}} raised on GitHub.}
    %         \resumeItem{Collaborated with the maintainer of the project to add features \& remove bugs, written in React and GoLang.}
    %           \resumeItem  {\textcolor{blue}{Tech Stack} \emph{GoLang, React, SQLite}}
    %       \resumeItemListEnd 
         
    %   \vspace{+6pt}
     

       
        \resumeSubHeadingListEnd
        
%-----------PROJECTS-----------
\section{\Large \textcolor{blue}{Projects}}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Airbnb Booking Analysis} - Python, Pandas, Matplotlib, Seaborn \href{https://github.com/singh05sumit/Capstone-EDA-Project-Airbnb-Booking-Analysis}{\textbf{\textcolor{gray}{GitHub}}}}
          
          \resumeItemListStart
            \resumeItem{Performed in-depth \textbf{\textcolor{black}{Exploratory Data Analysis (EDA)}} on Airbnb booking data, using \textbf{\textcolor{black}{Python}} and \textbf{\textcolor{black}{Pandas}} to clean, transform, and analyze datasets. Uncovered significant trends in guest booking patterns and pricing strategies.}
            \resumeItem{Developed insightful visualizations with \textbf{\textcolor{black}{Matplotlib}} and \textbf{\textcolor{black}{Seaborn}}, highlighting key factors such as seasonal demand variations across various locations, resulting in a \textbf{\textcolor{black}{15\%}} increase in booking accuracy predictions.
}
            \resumeItem{Delivered strategic recommendations to improve listing performance and maximize revenue, empowering hosts with
data-driven insights for better decision- making and competitive positioning.}
            }
          \resumeItemListEnd

        % VITA rest API project
          \vspace{-10pt}
          \resumeProjectHeading
          {\textbf{HR Analytics Dashboard} - Power Query Editor, Power  BI  \href{https://https://github.com/singh05sumit/HR_Analytics_Dashboard}{\textbf{\textcolor{gray}{GitHub}}}}
           
          \resumeItemListStart
            \resumeItem{Designed and implemented an \HR Analytics Dashboard in \textbf{\textcolor{black}{Power BI}}, tracking \textbf{\textcolor{black}{Key Performance Indicators (KPI)}} such as employee count, attrition rates, and job satisfaction.
}
            \resumeItem{Developed interactive visualizations, including \textbf{\textcolor{black}{Bar Graphs}}, \textbf{\textcolor{black}{Donut Charts}} and \textbf{\textcolor{black}{Area Charts}} using statistical methods to analyze and compare KPIs related.
}
            \resumeItem{Created trendlines and target lines within the dashboard, enabling HR teams to monitor progress against KPIs and achieve a \textbf{\textcolor{black}{25\% reduction}} in unplanned turnover by identifying and addressing key attrition factors.
.}
            
            \vspace{+8pt}
          \resumeItemListEnd
        %   CODE FORCES DIARY PROJECT
              \vspace{-20pt}
          
              \resumeItemListEnd           
              \resumeSubHeadingListEnd
\vspace{12pt}
        
       
        %-----------EDUCATION-----------
    \section{\Large \textcolor{blue}{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tolani Maritime Institute (University - BITS PILANI)}{Pune, Maharastra}
      {B.Tech. Marine Engineering }{Aug 2013 -- Aug 20177}
    
      \vspace{-18pt} 
      \resumeSubheading{}{}  
      
      
  \resumeSubHeadingListEnd
    \end{document}