%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Sumit Singh} \\ \vspace{5pt}
     \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +(91)9870177363 ~ \href{mailto:sumitsinghtp304@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{sumitsinghtp304@gmail.com}} ~ 
    \href{https://linkedin.com/in/sumit-singh304/}{\raisebox{-0.2\height}\faLinkedin\ \underline{sumit-singh304}}  ~
    \href{https://github.com/singh05sumit}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/singh05sumit}}
    \vspace{-8pt}
\end{center}\vspace{+10pt}


%-----------EDUCATION-----------
\section{Technical Skills}
\vspace{2pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages and Databases}{: Python, PostgreSQL} \\
     \vspace{4pt}
     \textbf{Libraries}{: Pandas, Numpy, Matplotlib, Seaborn, Scikit-Learn} \\
     \vspace{4pt}
     \textbf{Visualization Tools}{: Advance Excel, Microsoft Power BI} \\
     \vspace{4pt}
     \textbf{Data Analysis Skills}{: Data Wrangling, Exploratory Data Analysis, Data Visualization, Applied Statistics, Machine Learning Basics, ETL}
    }}
 \end{itemize}
 
%------RELEVANT COURSEWORK-------



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Workgen Solution Pvt. Ltd.}{ June 2022 -- Nov 2022}
      {Operation Executive}\
      \resumeItemListStart
        \resumeItem{Maintained daily workforce records and compiled comprehensive reports,resulting in improvement in data accuracy for senior management’s decision making.}
        \resumeItem{Conducted background verifications for over 125,000 + new and current employees, reducing theft and criminal activity and improving overall security by 30 \% at industrial premises.}
        \resumeItem{Analyzed and monitored shifts data to confirm slot availability for over 50,000+ store workers, leading to a 25 \% reduction in logistical and shift change issues.}
        
      \resumeItemListEnd
      \vspace{6pt}

    \resumeSubheading
      {Mitsui O.S.K. Lines Pvt. Ltd.}{Aug 2017 -- Jan 2019}
      {Assistant Engineer}{}
      \resumeItemListStart
        \resumeItem{Engineered daily operations of ship machinery as a Junior Engineer on a container vessel,enhancing system performance and reducing downtime by 20 \% .}
        \resumeItem{Participated in all safety and environmental drills as directed by the Captain, ensuring compliance and enhancing overall
emergency preparedness.}
        \resumeItem{Diagnosed and resolved critical issues during a scheduled maintenance period of engine room machinery, collaborating with senior engineers to achieve 100 \% operational efficiency and prevent project delays..}
        
    \resumeItemListEnd
    \vspace{6pt}
    
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section {Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Airbnb Booking Analysis} - Python, Pandas, Matplotlib, Seaborn \href{https://github.com/singh05sumit/Capstone-EDA-Project-Airbnb-Booking-Analysis}{\textbf{\textcolor{gray}{GitHub}}}}
          
          \resumeItemListStart
            \resumeItem{Performed in-depth Exploratory Data Analysis (EDA) on Airbnb booking data, using Python and Pandas to clean, transform, and analyze datasets. Uncovered significant trends in guest booking patterns and pricing strategies.}
            \resumeItem{Developed insightful visualizations with Matplotlib and Seaborn, highlighting key factors such as seasonal demand variations across various locations, resulting in a black increase in booking accuracy predictions.}
}
            \resumeItem{Delivered strategic recommendations to improve listing performance and maximize revenue, empowering hosts with
data-driven insights for better decision- making and competitive positioning.}
            }
          \resumeItemListEnd

        % VITA rest API project
          \vspace{-10pt}
          \resumeProjectHeading
          {\textbf{HR Analytics Dashboard} - Power Query Editor, Power  BI  \href{https://https://github.com/singh05sumit/HR_Analytics_Dashboard}{\textbf{\textcolor{gray}{GitHub}}}}
           
          \resumeItemListStart
            \resumeItem{Designed and implemented an HR Analytics Dashboard in Power BI, tracking Key Performance Indicators (KPI) such as employee count, attrition rates, and job satisfaction.}
}
            \resumeItem{Developed interactive visualizations, including black Bar Graphs, Donut Charts and Area Charts using statistical methods to analyze and compare KPIs related.}
}
            \resumeItem{Created trendlines and target lines within the dashboard, enabling HR teams to monitor progress against KPIs and achieve a 25\% reduction in unplanned turnover by identifying and addressing key attrition factors.}
.}
            
            \vspace{+8pt}
          \resumeItemListEnd
        %   CODE FORCES DIARY PROJECT
              \vspace{-20pt}
          
              \resumeItemListEnd           
              \resumeSubHeadingListEnd
\vspace{12pt}


%
%-----------EDUCATION SKILLS-----------

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tolani Maritime Institute (University - BITS PILANI)}{Aug. 2013 -- Aug 2017}
      {Bachelor of Technology in Marine Engineering}{Pune, Maharashtra}
  \resumeSubHeadingListEnd

\vspace{-18pt}


\end{document}
